
## Part 3: Association Rules


METRIC OF SUCCESS
Build an algotithm/model that is able to predict what a customer is going to buy from their previous purchases


## Loading our dataset


```{r}
head(Supermkt)

```

```R
# Then we install the required arules library 
#
install.packages("arules")
library(arules)
```
#Reloading our dataset as transactions

```{r}
path <- "http://bit.ly/SupermarketDatasetII"
Transactions<-read.transactions(path, sep = ",")
Transactions

```


```R
# Verifying the object's class
# ---
# This should show us transactions as the type of data that we will need
# ---
# 
class(Transactions)
```

```R
# Previewing our first 10 transactions
#
inspect(Transactions[1:10])
```

```R
# previewingcitems that make up our dataset,
# 
# ---
# 
items<-as.data.frame(itemLabels(Transactions))
colnames(items) <- "Item"
head(items, 10)    
```
```{r}
#Geberating summary of the transactions 

summary(Transactions)
```


```{r}
# Exploring the frequency of some articles 
# and getting percentage comparison to the total transactions
# 
itemFrequency(Transactions[, 8:10],type = "absolute")
round(itemFrequency(Transactions[, 8:10],type = "relative")*100,2)
```
Here we can infer that the products are between the 8th and the 10th transaction 
are the one below while black tea is purchased most making 1.43% of total purchases



```R
# Producing a chart of frequencies and filtering 
# to consider only items with a minimum percentage 
# of support/ considering a top x of items
# ---
# Displaying top 10 most common items in the transactions dataset 
# and the items whose relative importance is at least 10%
# 
par(mfrow = c(1, 2))

# plot the frequency of items
itemFrequencyPlot(Transactions, topN = 10,col="darkgreen")
itemFrequencyPlot(Transactions, support = 0.1,col="darkred")
```
The plots are quite congested hence we are not able to gain much insight from them but we can see different items and their frequency of purchase 


```{r}
```R
# Building a model based on association rules 
# using the apriori function 
# ---
# We use Min Support as 0.001 and confidence as 0.9
# ---
# 
rules <- apriori (Transactions, parameter = list(supp = 0.001, conf = 0.9))
rules

```
```
Our model got us a total of 11 rules this is because we used a high confidence interval 
which is optimal to ensure we have a right amount of rules that we can work with

## Nxet we try get the summary of these rules we got

```{r}
summary(rules)
```


```R
# Observing rules built in our model i.e. first 5 model rules
# ---
# 
inspect(rules[1:5])


From the inspection above we can conclude that with a 95%confidence interval if 
a customer buys red wine and soup they are also highly likely to buy mineral water
this insight can help supermarkets buy making sure these aisles are close to each other 
to easily capture these customers



